Dominance Regions for Affine Cluster Algebras

### 2022-06-21 affine_dominance.tex
An interesting observation at the end of section 5

  This would imply that the $\bfc$-vector part of every $E^{t_j}_{k,\varepsilon_j}$ vanishes by Lemma~\ref{lem:tropical signs}, can this be right?

>>>>

  \begin{lemma}
    For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of  
    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
    stabilizes after the first $n$ mutations.
  \end{lemma}
  \begin{proof}
    If the sequence is sink adapted, the coefficient part is always just zero.

    For a source adapted sequence, this should follow from an explicit calculation.
  \end{proof}
